---
title: "Stan_results"
author: "Alan"
date: "1 Maerz 2019"
output:
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
knitr::opts_chunk$set(fig.width=12, fig.height=8) 
knitr::opts_chunk$set(warning=FALSE) 



library(ggplot2)
library(tidyr)
library(dplyr)
library(gridExtra)
library(knitr)
library(rstan)
library(DT)


ind_res_tabs <- function(stan_model_list){
  res <- NULL
  for(i in 1:nrow(results)){
    res[i] <- paste0( '###  ', paste0(with(data.frame(t(rbind( names(results[,1:4]),c(results[i,1:4]),rep("\n",4)))), paste0(X1,X2,X3),rep("\n",4)),collapse=" "), " \n",
    "```{r individual_res",i,", results = 'asis'}", "\n",
    "ind_levels<-extract_individual_levels(stan_model_list[[",i,"]],ind_names[!is.na(mean_result[",i,",])]);
  
colnames(ind_levels)<-c('L','M','H','paramter','ID')
ind_levels %>% mutate(paramter = factor(paramter, levels = levels(factor(paramter))[c(7,8,3,4,6,5,2,1)] )) %>%
 ggplot(aes(x=ID,y=M))+geom_point()+
  geom_linerange(aes(ymin=L,ymax=H))+coord_flip()+
  facet_grid(.~paramter,scales  = 'free')+
  #geom_hline(data=pop_lvl,aes(yintercept=Median),color='blue',linetype='dashed')+
  labs(y='Regression parameters')", "\n",
    '```', '\n\n')
  }
  return(res)
}


fit_tabs <- function(ind_res, mean_result,data_stan,fake_data_list){
  res <- NULL
  for(i in 1:nrow(results)){
    res[i] <- paste0( '###  ', paste0(with(data.frame(t(rbind( names(results[,1:4]),c(results[i,1:4]),rep("\n",4)))), paste0(X1,X2,X3),rep("\n",4)),collapse=" "), " \n",
    "```{r, results = 'asis'}", "\n",
    "plot_effects(ind_res[[",i,"]],mean_result[",i,",],data_stan,fake_data_list[[",i,"]])", "\n",
    '```', '\n\n')
  }
  return(res)
}

include_model=1
make.tabs_prediction <- function(fake_data_list){
  res <- NULL
  for(i in 1:nrow(results)){#!!!!1:nrow(results)
    data = fake_data_list[[i]]
    res[i] <- paste0( '###  ', paste0(with(data.frame(t(rbind( names(results[,1:4]),c(results[i,1:4]),rep("\n",4)))), paste0(X1,X2,X3),rep("\n",4)),collapse=" "), " \n",
    "```{r pred",i,", results = 'asis'}", "\n",'include_model=1;ind_fits=ind_res[[',i,']];data=data.frame(fake_data_list[[',i,']]);',
    'source("Fig_1F.r");',
    'source("Figure_2A-D.r");',
     '\n',
    '```', '\n\n')
  }
  return(res)
}



trace_tabs <- function(stan_model_list){
  res3 <- NULL
  for(i in 1:nrow(results)){
    res3[i] <- paste0( '###  ', paste0(with(data.frame(t(rbind( names(results[,1:4]),c(results[i,1:4]),rep("\n",4)))), paste0(X1,X2,X3),rep("\n",4)),collapse=' '), ' \n',
    '```{r trace',i,', results = "asis",results="hide", message=FALSE, warning=FALSE}', '\n',
                      'traceplot(stan_model_list[[',i,']],pars=parent_names)', '\n',
                      '```', '\n\n')
  }
  return(res3)
}




trace_tabs_ind <- function(stan_model_list){
  res2 <- NULL
  for(i in 1:nrow(results)){
    res2[i] <- paste0( '###  ', paste0(with(data.frame(t(rbind( names(results[,1:4]),c(results[i,1:4]),rep("\n",4)))), paste0(X1,X2,X3),rep("\n",4)),collapse=' '), ' \n',
    '```{r trace_ind',i,', results = "asis",results="hide", message=FALSE, warning=FALSE}', '\n',
          'vars=rep(c("var_own","var_social","distance_weight","stay_intercept", "stay_dist","prox_weight","copy_intercept", "copy_dist")[!is.na(mean_result[',i,',])],each=3);',
          'indexs=rep(sample(unique(data_stan$ID),size=3),length(vars));',
             'vars2=apply(rbind(vars,"[",indexs,"]"),2,paste0,collapse ="");',
                      'traceplot(stan_model_list[[',i,']],pars=vars2)', '\n',
                      '```', '\n\n')
  }
  return(res2)
}





output_tabs <- function(stan_model_list){
  res4 <- NULL
  for(i in 1:nrow(results)){
    res4[i] <- paste0( '###  ', paste0(with(data.frame(t(rbind( names(results[,1:4]),c(results[i,1:4]),rep("\n",4)))), paste0(X1,X2,X3),rep("\n",4)),collapse=" "), " \n",
    "```{r text",i,", results = 'asis'}", "\n",
                      'datatable(round(summary(stan_model_list[[',i,']],pars=parent_names[!is.na(result[',i,',])])$summary,2))', "\n",
                      '```', '\n\n')
  }
  return(res4)
}
#

#plot_effects(result[16,],data_stan,fake_data_list[[16]])
#traceplot(stan_model_list[[16]],pars=colnames(result)[!is.na(result[16,])])
#data=data.frame(fake_data_list[16]);source("run_plot.R");source("Figure 3.R")

```



```{r show}
print(name)

datatable(results, rownames = FALSE, filter="top", options = list(pageLength = 8, scrollX=T) )

loos


#for(i in 1:nrow(results)){
#  datatable(print(stan_model_list[[i]],pars=colnames(result)[!is.na(result[i,])]))}

```


```{r showplot}


deltas = (-c(results$looic[results$distance_Weighting==1]-results$looic[results$distance_Weighting==0],
results$looic[results$peer_proximity==1]-  results$looic[results$peer_proximity==0],
results$looic[results$staying_probability==1]-  results$looic[results$staying_probability==0],
results$looic[results$copying_probability==1]-  results$looic[results$copying_probability==0]))

deltas_names= c(rep("Confirmation",8),rep("Proximity",8),rep("Stay",8),rep("Copy",8))




par(cex.lab=1.5, cex.axis=1.5, las=1, lend=1, yaxs='i',mfrow=c(1,1))#, xaxs='i'
plot(0, type='n', ylim=c(0.3,5), xlim=c(min(deltas,na.rm=T)-10,max(deltas,na.rm=T)+10), axes=FALSE,xlab='',ylab='')
axis(1, at=seq(round(min(deltas,na.rm=T),-1),max(deltas,na.rm=T),10))#, labels=FALSE
cols<-c("#1E90FF","#CD2626","#56ae6c","#ac9c3d","grey80")
level_names = unique(deltas_names)
	#individual data points
	for (k in 1:4){
	  k1 = rep(5-k,8)
		# summary stats per treatment
	y<-mean(deltas[deltas_names==level_names[k]], na.rm=T)
	
	w<-summary(deltas[deltas_names==level_names[k]])
	IQR<-w[5]-w[2]
	se<- sd(deltas[deltas_names==level_names[k]])/sqrt(length(deltas[deltas_names==level_names[k]]))	
	#interquartile
	rect(w[2],k1-0.3,w[5],k1+0.3,col=adjustcolor(cols[k], alpha=0.1))
	arrows(w[2]-1.5*IQR,k1,w[2],k1, code=0)
	arrows(w[5],k1,w[5]+1.5*IQR,k1, code=0)
	
	#median
	arrows(w[3], k1-0.3, w[3], k1+0.3, lwd=5, code=0)
	
	
	
		points(deltas[deltas_names==level_names[k]],k1, pch=16, col=cols[k])
		abline(v=0, , col = "lightgray",lty=2,cex=2)

	}





```

## Results (click through tabs to inspect models with or without specific strategies)



## Predictions: {.tabset .tabset-fade}
`r paste(knit(text = make.tabs_prediction(fake_data_list)))`
Upper panel: The colored bars indicate the avarage snesitivity of each individual. The red and green dots the average sensitivity of all choices for the empirical data and model predicitons respectively.  

## The fitted paramters: {.tabset .tabset-fade}
`r paste(knit(text = fit_tabs(ind_res, mean_result,data_stan,fake_data_list)))`

The fitted paramters with black lines indicating the fittings. The red lines ind the upper panels indicate the staying and copying probabilities including the baysian inference process.





## The summary: {.tabset .tabset-fade}
`r paste(knit(text = output_tabs(stan_model_list)))`





## The markow Chains: {.tabset .tabset-fade}
`r paste(knit(text = trace_tabs(stan_model_list)))`


## The individual markow Chains: {.tabset .tabset-fade}
`r paste(knit(text = trace_tabs_ind(stan_model_list)))`


## The individual results: {.tabset .tabset-fade}
`r paste(knit(text = ind_res_tabs(stan_model_list)))`



</div>


### The Stan Code: 
```{r show2}

print(cat(with_wighting_and_stay_model))
"The MCMC chains showing the posterior probabilities if the paramters. If the different chains are laying above each other they converged (which is good).







"

```

